Novelty Detection for Semantic Place Categorization

### 2011-07-14 thesis/presentation.tex
more updates

\documentclass[compress]{beamer}
\usepackage{default}
\usepackage{graphics}
\usepackage{ulem}
\usepackage{multicol}

\useinnertheme{rounded}
\usecolortheme{whale}
\useoutertheme[subsection=false]{miniframes}

@@

\begin{block}{Focus on Detection of Novel Semantic Categories of Places}

\end{block}
\note{
- It is unrealistic to believe on the possibility to describe all the required knowledge

@@

\subsection{Semantic Mapping}
\begin{frame}{Mapping - Machine Friendly}
\begin{columns}[c]
\column{0.5\textwidth}
  \begin{figure}
    \includegraphics[width=\textwidth]{figures/machinefriendly.jpg}
  \end{figure}

@@

\begin{frame}{Semantic Mapping}
\begin{columns}[c]

@@

\subsection{Novelty Detection as Thresholding}
\begin{frame}{Novelty Detection via Thresholding}

@@

\begin{block}{Conditional and Unconditional Probability Ratio}
\[P(\overline{novel}|x) = \frac{P(x|\overline{novel})P(\overline{novel})}{P(x)} \propto \frac{P(x|\overline{novel})}{P(x)}\]
\end{block}
\note{
Going back to a definition of a novelty detector, it can be shown that any optimal
detector can be seen as a solving a continuous knapsack problem, and that a threshold
can be set over the order relation defined by the probability of a sample being novel.
}
\end{frame}

@@

\subsection{Results}
\begin{frame}{Results}
  \begin{figure}
    \includegraphics[width=0.7\textwidth]{results/synthetic-all.pdf}
  \end{figure}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
\end{frame}

\subsection{Limitations}
\begin{frame}{Limitations}
\begin{itemize}
\item Incorporate structural information (non const P(novel))
\item Incorporate uncertain sensing
\end{itemize}
\end{frame}

\subsection{Future Work}
\begin{frame}{Future Work}
\begin{itemize}
\item Generalize the Framework
\item Exploiting Generative Models
\item Learning Graph Structures
\item After Detection of Knowledge Gaps
\end{itemize}
\end{frame}

\subsection{Extra Information}
\begin{frame}{Extra}
\begin{block}{Reproducible Research}
All produced results reproducible from online repository:
\url{https://github.com/andresusanopinto/novelty-detection-thesis}
\end{block}

\begin{block}{Article on EPIA 2011}
Part of this thesis work will be presented in EPIA 2011 (October)
\emph{Novelty Detection Using Graphical Models for
Semantic Room Classification}
\end{block}
\end{frame}

>>>>

\documentclass[compress]{beamer}
\usepackage[utf8x]{inputenc}
\usepackage{default}
\usepackage{graphics}
\usepackage{ulem}
\usepackage{multicol}

\useinnertheme{rounded}
\usecolortheme{whale}
\useoutertheme[subsection=false]{miniframes}
\setbeamertemplate{footline}[frame number]
\beamertemplatenavigationsymbolsempty

@@

\begin{block}{Focus on Semantic Categories of Places}
Humans attribute meaning to the areas that describe the expected properties,
objects and actions of them. E.g.\ cups are found in kitchens. 
\end{block}
\note{
- It is unrealistic to believe on the possibility to describe all the required knowledge

@@

\subsection{Mapping}
\begin{frame}{Mapping - Machine Friendly}
\begin{columns}[c]
\column{0.5\textwidth}
  \begin{figure}
    \includegraphics[width=\textwidth]{figures/machinefriendly.jpg}
  \end{figure}

@@

\subsection{Semantic Mapping}
\begin{frame}{Semantic Mapping}
\begin{columns}[c]

@@

\subsection{Thresholding}
\begin{frame}{Novelty Detection via Thresholding}

@@

\begin{block}{Conditional and Unconditional Probability Ratio}
\[P(\overline{novel}|x) = \frac{P(x|\overline{novel})P(\overline{novel})}{P(x)} \propto \frac{P(x|\overline{novel})}{P(x)}\]
\uncover<2>{\alert{Simplified with an assumption on constant $P(novel)$}}
\end{block}
\note{
Going back to a definition of a novelty detector, it can be shown that any optimal
detector can be seen as a solving a continuous knapsack problem, and that a threshold
can be set over the order relation defined by the probability of a sample being novel.
}
\end{frame}

@@

\subsection{Results}
\begin{frame}{Synthetic Dataset}

\begin{frame}{Results}
  \begin{figure}
    \includegraphics[width=0.7\textwidth]{results/synthetic-all.pdf}
  \end{figure}
\end{frame}

\section{Conclusion}

\subsection{Summary}
\begin{frame}{Summary}
\begin{itemize}
\item Studies a semantic mapping process
\item Studies novelty detection
\item Proposes a method to perform detection of novel categories
      of a variable type of a graphical model when the graph structure
      is dynamic.
\end{itemize}
\end{frame}

\subsection{Limitations}
\begin{frame}{Limitations}
\begin{block}{Assumption on constant $P(novel)$}
Graph structure plays a role on the likelihood a sample with a novel
category is drawn. Assuming it to be constant is a very strong assumption
that is not expected to hold in all scenarios.
\end{block}
%\begin{block}{Uncertain Sensing}
%The presented methods require calculation of normalized probabilities turning it impossible
%to handle implicit factors.
%\end{block}
\end{frame}

\subsection{Future Work}
\begin{frame}{Future Work}
  \begin{block}{Generalize the Framework}
  Handle novelty on any and more than one variable of the graph and fusing
  all novelty information in a single method in a probabilistic fashion (e.g.\ MAP operation).
  \end{block}
  \begin{block}{Exploit Generative Models}
  Develop methods to be able to explain what the system considers to be known or novel.
  Such that the reason causing novelty can be interpreted.
  \end{block}
\end{frame}
\begin{frame}{Future Work}
  \begin{block}{Learning Graph Structures}
  Graph structure should be considered probabilistic. Methods to handle and probabilistic
  represent knowledge on how the agent detect structures must be develop.
  \end{block}
  \begin{block}{After Detection of Knowledge Gaps}
  What can be done with the detection of novel situations? Can the system be adapted
  to learn and group novel situations? How to perform self-extension?
  \end{block}
\end{frame}

\subsection{Extra Information}
\begin{frame}{Extra}
\begin{block}{Reproducible Research}
All reports and results reproducible from online repository:
\url{https://github.com/andresusanopinto/novelty-detection-thesis}
\end{block}

\begin{block}{Article on EPIA 2011}
\textit{Novelty Detection Using Graphical Models for Semantic Room Classification}
\end{block}
\end{frame}
